weather

### 2021-08-13 data analysis/Analysis.Rmd
as

>>>>

```{r eval=FALSE}
adaptation_weather %>% 
  filter(month %in% c(6, 7, 8, 9)) %>% 
  group_by(month_lab, site, year) %>% 
  summarise(pp = sum(pp)) %>% 
  mutate(year = as.character(year),
         highlight = ifelse(year %in% c("2018", "2019"), TRUE, FALSE),
         variable = if_else(highlight == TRUE, year, "NA")) %>% 
  ggplot(aes(x = month_lab, y = pp)) +
  geom_jitter(aes(color = variable), alpha = 0.2) +
  scale_color_manual(values = c("red", "blue", "gray90")) +
  geom_line(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2018)) %>% 
               group_by(site, month_lab) %>% 
               summarise(pp = sum(pp)),
             mapping = aes(x = month_lab, y = pp, group = 1), 
             color = "red") +
  geom_line(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2019)) %>% 
               group_by(site, month_lab) %>% 
               summarise(pp = sum(pp)),
             mapping = aes(x = month_lab, y = pp, group = 1), 
             color = "blue") +
  geom_point(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2018)) %>% 
               group_by(site, month_lab) %>% 
               summarise(pp = sum(pp)),
             mapping = aes(x = month_lab, y = pp), 
             fill = "red", shape = 21, size = 3) +
  geom_point(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2019)) %>% 
               group_by(site, month_lab) %>% 
               summarise(pp = sum(pp)),
             mapping = aes(x = month_lab, y = pp), 
             fill = "blue", shape = 21, size = 3) +
  geom_richtext(data = text3, aes(x = 2.6, y = 330), 
            label = "Monthly sum precipitation <br>in <b style='color:red;'>2018</b> and <b style='color:blue;'>2019</b>", size = 2, 
            label.color = NA, fill = NA) +
  geom_richtext(data = text4, aes(x = 3.6, y = 320), 
            label = "30 years <br>monthly sum <br>precipitation", size = 2, 
             label.color = NA, fill = NA, color = "gray90") +
  geom_curve(data = text4, 
             x = 2.6, y = 310, 
             xend = 2, yend = 320,
             arrow = arrow(length = unit(0.07, "inch")), 
             size = 0.4, curvature = -0.3, color = "gray90") + 
  facet_grid(~ site) +
  labs(x = NULL, y = "Precipitation (mm)") +
  theme_test() +
  theme(legend.position = "none",
        strip.text = element_markdown(size = 25),
        axis.text.y = element_markdown(size = 25),
        axis.title = element_markdown(size = 25),
        axis.text.x = element_markdown(size = 25),
        legend.text = element_markdown(size = 25)) -> ppp

ggsave("ppp.png", height = 3, width = 6)
```

### 2021-08-13 data analysis/weather/weather.Rmd
as

```{r}
adaptation_weather %>% 
  filter(month %in% c(6, 7, 8, 9)) %>% 
  mutate(year = as.character(year),
         highlight = ifelse(year %in% c("2018", "2019"), TRUE, FALSE),
         variable = if_else(highlight == TRUE, year, "NA")) 
```

```{r}
text1 <- tibble(site = "Arlington")
text2 <- tibble(site = "Clay Center")
```

```{r}
adaptation_weather %>% 
  filter(month %in% c(6, 7, 8, 9)) %>% 
  mutate(year = as.character(year),
         highlight = ifelse(year %in% c("2018", "2019"), TRUE, FALSE),
         variable = if_else(highlight == TRUE, year, "NA")) %>% 
  ggplot(aes(x = month_lab, y = tmean)) +
  geom_jitter(aes(color = variable), alpha = 0.05, shape = 0) +
  scale_color_manual(values = c("red", "blue", "gray90")) +
  geom_line(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2018)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean, group = 1), 
             color = "red") +
  geom_line(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2019)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean, group = 1), 
             color = "blue") +
  geom_point(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2018)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean), 
             fill = "red", shape = 22, size = 3) +
  geom_point(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2019)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean), 
             fill = "blue", shape = 22, size = 3) +
  geom_richtext(data = text1, aes(x = 2, y = 7), 
            label = "Mean air temperature <br>in <b style='color:red;'>2018</b> and <b style='color:blue;'>2019</b>", size = 2, 
            label.color = NA, fill = NA) +
  geom_richtext(data = text2, aes(x = 2.2, y = 10), 
            label = "30 years <br>daily mean <br>air temperature", size = 2, 
             label.color = NA, fill = NA, color = "gray90") +
  geom_curve(data = text2, 
             x = 2, y = 13, 
             xend = 2.5, yend = 16,
             arrow = arrow(length = unit(0.07, "inch")), 
             size = 0.4, curvature = -0.3, color = "gray90") + 
  facet_grid(~ site) +
  labs(x = NULL, y = "Temperature (C)") +
  theme_test() +
  theme(legend.position = "none") -> temp

@@

```{r}
text3 <- tibble(site = "Grant")
text4 <- tibble(site = "Lincoln")
```

```{r}
adaptation_weather %>% 
  filter(month %in% c(6, 7, 8, 9)) %>% 
  group_by(month_lab, site, year) %>% 
  summarise(pp = sum(pp)) %>% 
  mutate(year = as.character(year),
         highlight = ifelse(year %in% c("2018", "2019"), TRUE, FALSE),
         variable = if_else(highlight == TRUE, year, "NA")) %>% 
  ggplot(aes(x = month_lab, y = pp)) +
  geom_jitter(aes(color = variable), alpha = 0.2) +
  scale_color_manual(values = c("red", "blue", "gray90")) +
  geom_line(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2018)) %>% 
               group_by(site, month_lab) %>% 
               summarise(pp = sum(pp)),
             mapping = aes(x = month_lab, y = pp, group = 1), 
             color = "red") +
  geom_line(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2019)) %>% 
               group_by(site, month_lab) %>% 
               summarise(pp = sum(pp)),
             mapping = aes(x = month_lab, y = pp, group = 1), 
             color = "blue") +
  geom_point(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2018)) %>% 
               group_by(site, month_lab) %>% 
               summarise(pp = sum(pp)),
             mapping = aes(x = month_lab, y = pp), 
             fill = "red", shape = 21, size = 3) +
  geom_point(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2019)) %>% 
               group_by(site, month_lab) %>% 
               summarise(pp = sum(pp)),
             mapping = aes(x = month_lab, y = pp), 
             fill = "blue", shape = 21, size = 3) +
  geom_richtext(data = text3, aes(x = 2.6, y = 330), 
            label = "Monthly sum precipitation <br>in <b style='color:red;'>2018</b> and <b style='color:blue;'>2019</b>", size = 2, 
            label.color = NA, fill = NA) +
  geom_richtext(data = text4, aes(x = 3.6, y = 320), 
            label = "30 years <br>monthly sum <br>precipitation", size = 2, 
             label.color = NA, fill = NA, color = "gray90") +
  geom_curve(data = text4, 
             x = 2.6, y = 310, 
             xend = 2, yend = 320,
             arrow = arrow(length = unit(0.07, "inch")), 
             size = 0.4, curvature = -0.3, color = "gray90") + 
  facet_grid(~ site) +
  labs(x = NULL, y = "Precipitation (mm)") +
  theme_test() +
  theme(legend.position = "none") -> ppp

ggsave("ppp.png", height = 3, width = 6)
```

>>>>

```{r}
adaptation_weather %>% 
  filter(month %in% c(6, 7, 8, 9)) %>% 
  mutate(year = as.character(year),
         highlight = ifelse(year %in% c("2018", "2019"), TRUE, FALSE),
         variable = if_else(highlight == TRUE, year, "NA")) -> adaptation_weather1
```

```{r}
adaptation_weather1 %>% 
  filter(year %in% c(2018, 2019)) %>% 
  group_by(site, year, month) %>% 
  summarise(prec = sum(pp), tmax = mean(tmax), tmin = mean(tmin), tmean = mean(tmean)) %>% 
  mutate_if(is.double, ~round(., 1))
```

```{r}
adaptation_weather %>% 
  mutate(site = fct_recode(site, 
                           "Arlington, WI" = "Arlington",
                           "Clay Center, NE" = "Clay Center",
                           "Grant, NE" = "Grant",
                           "Lincoln, NE" = "Lincoln",
                           "Macomb, IL" = "Macomb")) -> adaptation_weather
```

```{r}
text1 <- tibble(site = "Arlington, WI")
text2 <- tibble(site = "Clay Center, NE")
```

```{r}
adaptation_weather %>% 
  filter(month %in% c(6, 7, 8, 9)) %>% 
  mutate(year = as.character(year),
         highlight = ifelse(year %in% c("2018", "2019"), TRUE, FALSE),
         variable = if_else(highlight == TRUE, year, "NA")) %>% 
  ggplot(aes(x = month_lab, y = tmean)) +
  geom_jitter(aes(color = variable), alpha = 0.05, shape = 0) +
  scale_color_manual(values = c("red", "blue", "gray90")) +
  geom_line(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2018)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean, group = 1), 
             color = "red") +
  geom_line(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2019)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean, group = 1), 
             color = "blue") +
  geom_point(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2018)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean), 
             fill = "red", shape = 22, size = 3) +
  geom_point(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2019)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean), 
             fill = "blue", shape = 22, size = 3) +
  geom_richtext(data = text1, aes(x = 2, y = 7), lineheight = 0.4, 
            label = "Mean air temperature <br>in <b style='color:red;'>2018</b> and <b style='color:blue;'>2019</b>", size = 6, 
            label.color = NA, fill = NA) +
  geom_richtext(data = text2, aes(x = 2.2, y = 10), lineheight = 0.4, 
            label = "30 years <br>daily mean <br>air temperature", size = 6, 
             label.color = NA, fill = NA, color = "gray90") +
  geom_curve(data = text2, 
             x = 2, y = 13, 
             xend = 2.5, yend = 16,
             arrow = arrow(length = unit(0.07, "inch")), 
             size = 0.4, curvature = -0.3, color = "gray90") + 
  scale_y_continuous(limits = c(0, 32)) +
  facet_grid(~ site) +
  labs(x = NULL, y = "Temperature (C)") +
  theme_test() +
  theme(legend.position = "none",
        strip.text = element_markdown(size = 28),
        axis.text.y = element_markdown(size = 25),
        axis.title = element_markdown(size = 27),
        axis.text.x = element_markdown(size = 25),
        legend.text = element_markdown(size = 25))  -> temp

@@

```{r}
text3 <- tibble(site = "Grant, NE")
text4 <- tibble(site = "Lincoln, NE")
```

```{r}
adaptation_weather %>% 
  filter(month %in% c(6, 7, 8, 9)) %>% 
  group_by(month_lab, site, year) %>% 
  summarise(pp = sum(pp)) %>% 
  mutate(year = as.character(year),
         highlight = ifelse(year %in% c("2018", "2019"), TRUE, FALSE),
         variable = if_else(highlight == TRUE, year, "NA")) -> adaptation_pp
```

```{r message = FALSE, warning = FALSE}
adaptation_pp %>% 
ggplot(aes(x = month_lab, y = pp)) +
  geom_bar(data = adaptation_pp %>% filter(year == c(2018, 2019)), 
           mapping = aes(fill = year),
           stat = "identity", position = "dodge", alpha = 1) +
  geom_point(data = adaptation_pp %>% filter(year != c(2018, 2019)), 
              position = position_jitter(seed = 1),
              alpha = 0.2, color = "gray50", 
              show.legend = FALSE) +
  scale_fill_manual(values = c("red", "blue")) +
  facet_grid(~ site) +
  geom_richtext(data = text3, aes(x = 2.6, y = 330), lineheight = 0.4, 
            label = "Monthly sum precipitation <br>in <b style='color:red;'>2018</b> and <b style='color:blue;'>2019</b>", size = 6, 
            label.color = NA, fill = NA) +
  geom_richtext(data = text4, aes(x = 3.6, y = 320), lineheight = 0.4, 
            label = "30 years <br>monthly sum <br>precipitation", size = 6, 
             label.color = NA, fill = NA, color = "gray90") +
  geom_curve(data = text4, 
             x = 2.6, y = 310, 
             xend = 2.1, yend = 320,
             arrow = arrow(length = unit(0.07, "inch")), 
             size = 0.4, curvature = -0.3, color = "gray90") + 
  labs(x = NULL, y = "Precipitation (mm)") +
  theme_test() +
  theme(legend.position = "none",
        strip.text = element_markdown(size = 28),
        axis.text.y = element_markdown(size = 25),
        axis.title = element_markdown(size = 27),
        axis.text.x = element_markdown(size = 25),
        legend.text = element_markdown(size = 25)) -> ppp

```
